Computable Poincar\'e--Friedrichs constants\\ for the $L^{p}$ de Rham complex over domains\\ with shellable triangulations

### 2024-09-11 main.tex
theo's annotations

% DONE : MV : remove 'For example' 
We illustrate the subject of our discussion with the curl operator. 
% One example application concerns the curl operator. 
If $\bff \in \bfL^{2}(\Omega)$ is a square-integrable vector field on some domain $\Omega \subseteq \bbR^3$, 
we want to find a potential $\bfu \in \bfL^2(\Omega)$ under the curl operator, i.e., $\curl \bfu = \bff$, such that the $\bfL^2$ norm of the potential is bounded in terms of the source field $\bff$. 
This boundedness is expressed via the Poincar\'e--Friedrichs inequality 
\begin{align*}
    \min\limits_{ \substack{ \bfv \in \bfL^{2}(\Omega) \\ \curl \bfv = \bff } } \| \bfv \|_{L^{2}(\Omega)}
    \leq 
    C_{\curl}
    \| \bff \|_{L^{2}(\Omega)}
    .
\end{align*}
The constant in this inequality quantifies the stability properties of the Maxwell system on that domain. Any upper bound for it gives rise to a lower bound for the Maxwell eigenvalues.

@@

% DONE: MV : Be more didactical: write following as the existence of a potential. 
Given a domain $\Omega \subseteq \bbR^{n}$ and Lebesgue exponent $1 \leq p \leq \infty$,
we search for a constant $C_{\grad,\Omega,p} > 0$ such that the following holds:
for every gradient vector field $\bff \in \nabla W^{1,p}(\Omega)$ there exists a scalar potential $u \in W^{1,p}(\Omega)$
such that $\nabla u = \bff$ and 
\begin{align}\label{math:intro:inequalitypf:gradient}
    \| u \|_{L^{p}(\Omega)}
    \leq 
    C_{\grad,\Omega,p} 
    \| \bff \|_{L^{p}(\Omega)}
    .
\end{align}
We call this inequality \emph{Poincar\'e--Friedrichs inequality} and the constant $C_{\grad,\Omega,p}$ is called the \emph{Poincar\'e--Friedrichs constant} with exponent $p$. 
The different scalar potentials only differ by a constant. 
Therefore, %when the domain is connected, then 
this inequality is equivalent to the following statement: 
\begin{align}\label{math:intro:poincarefriedrichs:grad}
    \min\limits_{c\in\bbR}
    \| u - c \|_{L^{p}(\Omega)}
    \leq 
    C_{\grad,\Omega,p} \| \nabla u \|_{L^{p}(\Omega)},
    \quad 
    \forall
    u \in W^{1,p}(\Omega) % DONE: Use \forall notation 
    .\tag{PF} 
\end{align}
% Given a domain $\Omega \subseteq \bbR^{n}$ and Lebesgue exponent $1 \leq p \leq \infty$,
% we search for a constant $C_{\grad,\Omega,p} > 0$ such that 
% \begin{align}\label{math:intro:poincarefriedrichs:grad}
%     \min\limits_{c\in\bbR}
%     \| u - c \|_{L^{p}(\Omega)}
%     \leq 
%     C_{\grad,\Omega,p} \| \nabla u \|_{L^{p}(\Omega)},
%     \quad 
%     u \in W^{1,p}(\Omega) % DONE: Use \forall notation 
%     .\tag{PF} 
% \end{align}
Finding a potential of a given gradient $\nabla u$ is generally a nonlinear operation. 
The operator norm of any \emph{linear} potential construction is an upper bound for the Poincar\'e--Friedrichs constant. 
% Even though the existence of such a bounded linear potential construction is not evident a priori, picking the average-free potential 
One example for a bounded linear operator is the average-free potential:
\begin{align*}
    \Phi_{\grad}( \bff ) 
    := 
    \argmin\limits_{ \substack{ v \in W^{1,p}(\Omega) \\ \int_\Omega v = 0 } } \| \nabla v - \bff \|_{L^{p}(\Omega)},
    \quad 
    \forall 
    \bff \in \nabla W^{1,p}(\Omega)
    .
\end{align*} 
Its operator norm is the constant $C_{{\rm P},\Omega,p} > 0$ in the Poincar\'e inequality 
\begin{align}\label{math:intro:poincare:grad}
    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
    \leq 
    C_{{\rm P},\Omega,p} \| \nabla u \|_{L^{p}(\Omega)},
    \quad 
    \forall 
    u \in W^{1,p}(\Omega)
    , \tag{P} % DONE: tag Poincar\'e inequality 
\end{align}
where $u_\Omega$ denotes the average of $u$.
Considerable research effort has gone into finding (or estimating) the optimal constants in the Poincar\'e--Friedrichs inequalities~\eqref{math:intro:poincarefriedrichs:grad} or Poincar\'e inequalities~\eqref{math:intro:poincare:grad}.

Most research on optimal constants has addressed the case of convex domains. 
% The optimal constants that depend solely on the domain diameter are known if $p=2$ \cite{bebendorf2003note} and if $p=1$ \cite{acosta2004optimal}. 
Notably, if the constants are required to depend on the convex domain only via its diameter, 
then the optimal constants $C_{\grad,\Omega,p}$ for any $1 \leq p < \infty$ are known explicitly~\cite{bebendorf2003note,acosta2004optimal,esposito2013poincare,ferone2012remark}.
When the domain is not convex but star-shaped with respect to a ball,
then polynomial interpolation estimates already imply the Poincar\'e inequality~\cite{brenner2008mathematical,ern2021finite}. 
An open set star-shaped with respect to a internal point satisfies Poincar\'e inequalities~\cite[Theorem~3.1]{hurri1988poincare}.

@@

Not much attention seems to have been given to the study of optimal constants in such Poincar\'e--Friedrichs inequalities for the curl and divergence operators. 
% even if the domain is convex, 
This sharply contrasts to the study of the gradient operator. 
%
% The literature in functional analysis is much scarcer when it comes to any upper bounds for the Poincar\'e--Friedrichs constants. 
We can access some estimates from the literature in the formalism of exterior calculus. 
We are aware of work by Guerini and Savo~\cite{guerini2004eigenvalue},
% who estimate the Poincar\'e--Friedrichs constants over smoothly bounded convex domains in the Hilbert space setting, when $p=2$. 
who provide lower bounds for the spectrum of the Hodge--Laplace operator on smoothly bounded convex domains, 
thus giving upper bounds for the Poincar\'e--Friedrichs constant of the exterior derivative, and hence for the curl and divergence operators, when $p=2$.
By duality, that implies lower bounds for the case of full boundary conditions.
% They also provide sequences of inequalities, such as the following in 3D smoothly bounded convex domains:
% \begin{align}\label{math:intro:guerinisavo}
%     C_{\grad,\Omega,2} \geq C_{\curl,\Omega,2} \geq C_{\divergence,\Omega,2}.
% \end{align}
% We emphasize that \cite{guerini2004eigenvalue} only addresses smoothly bounded domains, but the extension to convex domains is a technicality.

@@

The main objective of this manuscript is bounding the Poincar\'e--Friedrichs constants over local stars within triangulated domains. 
Clearly, not all local stars describe convex subdomains. 
One possible avenue towards Poincar\'e--Friedrichs constants is the observation that local stars in triangulations are star-shaped with respect to a ball,
which enables tools such as averaged Poincar\'e and Bogovski\u{\i} operators. 
However, estimates that rely on this geometric condition deteriorate when the aforementioned ball has radius much smaller than the domain diameter. 
This is not as much a problem over patches around interior subsimplices, where the size of the interior ball only depends on the shape regularity of the triangulation. 
But that interior ball can be arbitrarily small when the patch is around a boundary simplex, even if the mesh has good shape regularity: 
this occurs when the domain has sharp reentrant corners, and some illustrative limit cases include the slit domain~\cite{veeser2012poincare} and the crossed bricks domain~\cite{licht2019smoothed}, % DONE: MV : find the examples in the paper by verfurth and veeser 
which contain finite element patches are not star-shaped with respect to any ball.

@@

% DONE: cite VVVV
In the Hilbert space case, $p=2$, and when the domain is smoothly bounded, the work of Guerini and Savo~\cite{guerini2004eigenvalue} shows that the Poincar\'e--Friedrichs constant for the gradient already estimates the corresponding constants for the curl and divergence operators. By duality, this also is an upper estimate of the Poincar\'e--Friedrichs constants for the gradient, curl, and divergence subject to Dirichlet, tangential, and normal boundary conditions, respectively, along the entire boundary. 
% These comparisons~\eqref{math:intro:guerinisavo} are restricted to convex smoothly bounded domains.

But no such results are known over convex Lipschitz domains and for general Lebesgue exponents $1 \leq p \leq \infty$, which is why we rely on regularized potential operators as a remedy. 
We follow closely the discussions by Costabel and McIntosh~\cite{costabel2010bogovskiui},
who study regularized Poincar\'e and Bogovski\u{\i}-type potential operators over domains star-shaped with respect to a ball. 
In comparison to their exposition, our variants of the regularized potential operators are simplified:
we only study them over convex domains and use simpler (that is, constant) weight functions. 
The resulting operator features generally lower regularity properties in comparison to the regularized potential in the literature;
however, their properties are sufficient for our purposes. We easily estimate their operator norms. 
We consider the latter outcome to be of independent interest.

In addition to that, we need to find potentials for the gradient, curl and divergence operators over a simplex subject to partial boundary conditions. 
Again, we want to address the entire range $1 \leq p \leq \infty$ of Lebesgue exponents. 
We are not aware of any explicit estimates in the literature and there are no regularized potential operators for these boundary conditions. 
The Poincar\'e--Friedrichs inequality subject to full boundary conditions is repurposed to prove Poincar\'e--Friedrichs inequalities for differential forms over simplices and subject to partial boundary conditions. 
For example, given the curl of a vector field over a tetrahedron that vanishes along, say, two of the tetrahedron faces, we want to find the unique vector field potential. We achieve this by constructing an auxiliary problem subject to full boundary conditions.
\\

% Exterior calculus % DONE: MV recommends moving this down to finish the current line of thoughts 
Though we present our results in vector calculus, our main arguments are given in the formalism of exterior calculus~\cite{greub1967multilinear,lee2012smooth}. Exterior calculus is used ubiquitously in the mathematical literature of physics and engineering and has found widespread adoption in the theoretical and numerical analysis for vector-valued partial differential equations~\cite{hiptmair2002finite,gross2004electromagnetic,arnold2006finite,arnold2009geometric,arnold2010finite,demlow2014posteriori,licht2021local,arnold2021complexes}. Loosely speaking, exterior calculus is the calculus of antisymmetric tensor fields. The formalism is independent of the dimension and highlights underlying geometric structures common to the gradient, curl, and divergence operators.
%It also enables us to leverage on the rich literature of Sobolev spaces of differential forms.
For the purpose of our discussion, this formalism allows us to leverage results from a larger body of literature in differential geometry and functional analysis. 
\\

% Future work 
Computable reliable estimates for the Poincar\'e--Friedrichs constant are important: 
they quantify the fundamental stability properties of partial differential equations in vector analysis,
such as the Hodge Laplace equation. 
Upper bounds correspond to lower bounds for the non-zero eigenvalues of the scalar and vector Laplacian.
% Furthermore, their constants enter the stability and convergence theory of finite element methods. 
In numerical methods, upper bounds for the Poincar\'e--Friedrichs constant enter the stability and convergence theory of finite element methods,
and they lead to lower bounds for the spectrum of finite element matrices. 
The are several avenues for further research going from here.

@@

Related to the first of the aforementioned opportunities for improvement, we conjecture that the Guerini--Savo estimates, hitherto only known for the exterior derivative as a mapping between Hilbert spaces and over smoothly bounded convex domains, could be extended to the entire range of Lebesgue exponents $1 \leq p \leq \infty$ and to convex Lipschitz domains. We believe such estimates would yield considerably better bounds on the Poincar\'e--Friedrichs constants than the regularized potential operators. 
% We conjecture that the Poincar\'e--Friedrichs constant for the gradient operator still bounds the Poincar\'e--Friedrichs constants of the other instances of the exterior derivatives, as in \eqref{math:intro:guerinisavo}, when $1 \leq p \leq \infty$ and the domain is convex. 
On a related note, explicit estimates for the operator norms of regularized potential operators with different degrees of smoothing are of general interest. 
These topics remain for future research.

@@

When $\calT$ is a triangulation and $T \in \calT$, then $\patch_{\calT}(T)$ denotes the \emph{local patch} or \textit{local star} of $T$, 
which the simplicial subcomplex of $\calT$ that contains all supersimplices of $T$ and their subsimplices. 
We write $\carapace_{\calT}(T)$ for the subset of the local patch whose members do not contain $T$ itself. 
Formally,
\begin{gather*}
    \patch_{\calT}(T) := \bigcup_{ T' \in \supsimplex(\calT,T) } \subsimplex(T'),
    \qquad 
    \carapace_{\calT}(T) := \bigcup_{ \substack{ T' \in \patch_{\calT}(T) \\ T \nsubseteq T' } } \subsimplex(T').
\end{gather*}
We write $U_T := | \patch_{\calT}(T) |$ for the underlying set of the local patch. 
A crucial observation is the following.

@@

We introduce a specific notion of connectivity. 
Given an $n$-dimensional simplicial complex $\calT$, 
we call $n$-simplices $S,S' \in \calT$ \emph{strongly connected in $\calT$} if there exists a sequence $S_0=S,S_1,\dots,S'=S_m \in \calT$ such that $S_{i} \cap S_{i-1}$ is a face of both $S_{i}$ and $S_{i-1}$ for all $1 \leq i \leq m$. 
We call such a sequence a \emph{strong path} from $S$ to $S'$ in $\calT$. 
Clearly, strongly connected in $\calT$ is an equivalence relation among simplices. 
A \emph{strongly connected component} of $\calT$ is an equivalence class under this equivalence relation, 
and we call $\calT$ \emph{strongly connected} if it has only one strongly connected component.

@@

We collect examples for Poincar\'e and Poincar\'e--Friedrichs inequalities for the important special case of convex domains; 
see also~\cite[Lemma~3.24]{ern2021finite} for a short overview. 
Over convex bounded domains, we have the Poincar\'e inequalities~\cite{bebendorf2003note,acosta2004optimal} 
\begin{align}\label{math:acostaduran}
    \| u - u_{\Omega} \|_{L^{1}(\Omega)}
    \leq 
    \frac{\diam(\Omega)}{2}
    \| \nabla u \|_{L^{1}(\Omega)}
    ,
    \quad 
    \forall 
    u \in W^{1,1}(\Omega)
    ,
    \\
    \| u - u_{\Omega} \|_{L^{2}(\Omega)} \label{math:bebendorf}
    \leq 
    \frac{\diam(\Omega)}{\pi}
    \| \nabla u \|_{L^{2}(\Omega)}
    ,
    \quad 
    \forall 
    u \in W^{1,2}(\Omega)
    .
\end{align}
These two estimates are the best possible Poincar\'e inequalities in the cases $p=1$ and $p=2$, respectively, in terms of the diameter alone. 
Upper bounds for the Poincar\'e constant over convex domains with $1 < p < \infty$ are known in the literature~\cite[Theorem~1.1, Theorem~1.2]{chua2006estimates}:
\begin{align}\label{math:chuawheeden}
    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
    \leq 
    C_{{\rm P},{\rm CW},p}
    \diam(\Omega)
    \| \nabla u \|_{L^{p}(\Omega)}
    ,
    \quad 
    \forall 
    u \in W^{1,p}(\Omega)
    ,
\end{align}
where we use an upper bound by Chua and Wheeden:
\begin{align*}
    C_{{\rm P},{\rm CW},p} 
    := 
    \sup\limits_{ v \in C^\infty([0,1]) \setminus \bbR } 
    \frac{ 
        \| v - v_{[0,1]} \|_{L^{p}([0,1])} 
    }{ 
        \| \nabla v \|_{L^{p}([0,1])} 
    }
    \leq 
    \sqrt[p]{p} 2^{1-\frac 1 p}
    =
    2
    \left( \frac p 2 \right)^{\frac 1 p}
    .
\end{align*}
Note that this upper bound is generally not optimal among the upper bounds that only depend on the domain diameter and the Lebesgue exponent.
As discussed above, these Poincar\'e inequalities imply Poincar\'e--Friedrichs inequalities.

@@

In this section we address the stepwise computable estimate of Poincar\'e--Friedrichs constants of triangulated domains. As a preparatory step, 
Given a gradient vector field, we can reconstruct the original scalar function up to a constant by a well-understood procedure: after fixing a starting point, we integrate the gradient vector field along lines emanating from that starting point. This defines a scalar potential. 
This serves as our inspiration for estimating the Poincar\'e constant over triangulated domains, which we achieve by an explicit construction of scalar potentials: 
after fixing a starting triangle, we construct a scalar potential for a given gradient vector field on larger and larger simplicial neighborhoods. 
The basic idea has appeared in the different variants before, for instance recently in \cite{Ern_Voh_p_rob_3D_20, Chaum_Voh_p_rob_3D_H_curl_23, Voh_loc_glob_H1_24}.
\\

@@

@@

\begin{example}
    Any simplex $T$ trivially has a shelling. The boundary complex $\partial \calT(T)$ has a shelling:
    in fact, any enumeration of the boundary faces of $T$ constitutes a shelling.
\end{example}
\begin{example}
    The standard triangulation of the $n$-dimensional cube by six tetrahedra, the Kuhn triangulation~\cite{kuhn1960some}, is shellable.\footnote{We remark that Kuhn attributes this triangulation to Lefschetz~\cite{lefschetz2015introduction}.}
\end{example}

@@

        By an application of Rademacher's theorem, we conclude that $\calK$ is bi-Lipchitz. 
        \color{black}

>>>>

% DONE : MV : remove 'For example' 
We illustrate the subject of our discussion with the curl operator. 
% One example application concerns the curl operator. 
If $\bff \in \bfL^{2}(\Omega)$ is a square-integrable vector field on some domain $\Omega \subseteq \bbR^3$, 
we want to find a potential $\bfu \in \bfL^2(\Omega)$ under the curl operator, i.e., $\curl \bfu = \bff$, such that the $\bfL^2$ norm of the potential is bounded in terms of the source field $\bff$. Specifically, we want the Poincar\'e--Friedrichs inequality % DONE: Theo prefers not using ``expressed''
\begin{align*}
    \min\limits_{ \substack{ \bfv \in \bfL^{2}(\Omega) \\ \curl \bfv = \bff } } \| \bfv \|_{L^{2}(\Omega)}
    \leq 
    C_{\curl}
    \| \bff \|_{L^{2}(\Omega)}
    .
\end{align*}
The constant in this inequality quantifies the stability properties of the Maxwell system on that domain. 
Any upper bound for it gives rise to a lower bound for the Maxwell eigenvalues.

@@

% DONE: MV : Be more didactical: write following as the existence of a potential. 
Given a domain $\Omega \subseteq \bbR^{n}$ and Lebesgue exponent $1 \leq p \leq \infty$,
we search for a constant $C_{\grad,\Omega,p} > 0$ such that the following holds:
for every gradient vector field $\bff \in \nabla W^{1,p}(\Omega)$ there exists a scalar potential $u \in W^{1,p}(\Omega)$
such that $\nabla u = \bff$ and 
\begin{align}\label{math:intro:inequalitypf:gradient} 
    \| u \|_{L^{p}(\Omega)}
    \leq 
    C_{\grad,\Omega,p} 
    \| \bff \|_{L^{p}(\Omega)}
    .
\end{align}
We call this inequality \emph{Poincar\'e--Friedrichs inequality} and the constant $C_{\grad,\Omega,p}$ is called the \emph{Poincar\'e--Friedrichs constant} with exponent $p$. 
The different scalar potentials only differ by a constant. 
Therefore, %when the domain is connected, then 
this inequality is equivalent to the following statement: 
\begin{align}\label{math:intro:poincarefriedrichs:grad}
    \min\limits_{c\in\bbR}
    \| u - c \|_{L^{p}(\Omega)}
    \leq 
    C_{\grad,\Omega,p} \| \nabla u \|_{L^{p}(\Omega)},
    \quad 
    \forall
    u \in W^{1,p}(\Omega) % DONE: Use \forall notation 
    .\tag{PF} 
\end{align}
% Given a domain $\Omega \subseteq \bbR^{n}$ and Lebesgue exponent $1 \leq p \leq \infty$,
% we search for a constant $C_{\grad,\Omega,p} > 0$ such that 
% \begin{align}\label{math:intro:poincarefriedrichs:grad}
%     \min\limits_{c\in\bbR}
%     \| u - c \|_{L^{p}(\Omega)}
%     \leq 
%     C_{\grad,\Omega,p} \| \nabla u \|_{L^{p}(\Omega)},
%     \quad 
%     u \in W^{1,p}(\Omega) % DONE: Use \forall notation 
%     .\tag{PF} 
% \end{align}
Finding a norm-minimizing potential of a given gradient $\nabla u$, if possible, is generally a nonlinear operation.\footnote{The existence of a minimum-norm potential is not guaranteed unless $1 < p < \infty$.}
The operator norm of any \emph{linear} potential construction serves as an upper bound for the Poincar\'e--Friedrichs constant. 
% Even though the existence of such a bounded linear potential construction is not evident a priori, picking the average-free potential 
One very simple example for such a bounded linear operator is the average-free potential: % DONE Theo : too much formalism. Solution: Acknowledge that it's very formal 
\begin{align*}
    \Phi_{\grad}( \bff ) 
    := 
    \argmin\limits_{ \substack{ v \in W^{1,p}(\Omega) \\ \int_\Omega v = 0 } } \| \nabla v - \bff \|_{L^{p}(\Omega)},
    \quad 
    \forall 
    \bff \in \nabla W^{1,p}(\Omega)
    .
\end{align*} 
Its operator norm is the constant $C_{{\rm P},\Omega,p} > 0$ in the Poincar\'e inequality 
\begin{align}\label{math:intro:poincare:grad}
    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
    \leq 
    C_{{\rm P},\Omega,p} \| \nabla u \|_{L^{p}(\Omega)},
    \quad 
    \forall 
    u \in W^{1,p}(\Omega)
    , \tag{P} % DONE: tag Poincar\'e inequality 
\end{align}
where $u_\Omega$ denotes the average of $u$.
Considerable research effort has gone into finding (or estimating) the optimal constants in the Poincar\'e--Friedrichs inequalities~\eqref{math:intro:poincarefriedrichs:grad} or Poincar\'e inequalities~\eqref{math:intro:poincare:grad}.

Most research on optimal constants has addressed the case of convex domains. 
% The optimal constants that depend solely on the domain diameter are known if $p=2$ \cite{bebendorf2003note} and if $p=1$ \cite{acosta2004optimal}. 
Notably, if the constants are required to depend on the convex domain only via its diameter, 
then the optimal constants $C_{\grad,\Omega,p}$ for any $1 \leq p < \infty$ are known explicitly~\cite{bebendorf2003note,acosta2004optimal,esposito2013poincare,ferone2012remark}.
When the domain is not convex but star-shaped with respect to a ball,
then polynomial interpolation estimates already imply the Poincar\'e inequality~\cite{brenner2008mathematical,ern2021finite}. 
Poincar\'e inequalities hold over star-shaped open sets~\cite[Theorem~3.1]{hurri1988poincare}. % DONE: strange sentence

@@

Not much attention seems to have been given to the study of optimal constants in such Poincar\'e--Friedrichs inequalities for the curl and divergence operators. 
% even if the domain is convex, 
This sharply contrasts to the study of the gradient operator. 
%
% The literature in functional analysis is much scarcer when it comes to any upper bounds for the Poincar\'e--Friedrichs constants. 
We can access some estimates from the literature in the formalism of exterior calculus. 
We are aware of work by Guerini and Savo~\cite{guerini2004eigenvalue},
% who estimate the Poincar\'e--Friedrichs constants over smoothly bounded convex domains in the Hilbert space setting, when $p=2$. 
who provide lower bounds for the spectrum of the Hodge--Laplace operator on convex domains with smooth boundary, % DONE: Theo : smoothly bounded -> with smooth boundary
thus giving upper bounds for the Poincar\'e--Friedrichs constant of the exterior derivative, and hence for the curl and divergence operators, when $p=2$.
By duality, that implies lower bounds for the case of full boundary conditions.
% They also provide sequences of inequalities, such as the following in 3D smoothly bounded convex domains:
% \begin{align}\label{math:intro:guerinisavo}
%     C_{\grad,\Omega,2} \geq C_{\curl,\Omega,2} \geq C_{\divergence,\Omega,2}.
% \end{align}
% We emphasize that \cite{guerini2004eigenvalue} only addresses smoothly bounded domains, but the extension to convex domains is a technicality.

@@

The main objective of this manuscript is bounding the Poincar\'e--Friedrichs constants over local stars within triangulated domains. 
Clearly, not all local stars describe convex subdomains. 
One possible avenue towards Poincar\'e--Friedrichs constants is the observation that local stars in triangulations are star-shaped with respect to a ball,
which enables tools such as averaged Poincar\'e and Bogovski\u{\i} operators~\cite{costabel2010bogovskiui}. 
However, estimates that rely on this geometric condition deteriorate when the aforementioned ball has radius much smaller than the domain diameter. 
This is not as much a problem over patches around interior subsimplices, where the size of the interior ball only depends on the shape regularity of the triangulation. 
But that interior ball can be arbitrarily small when the patch is around a boundary simplex, even if the mesh has good shape regularity: 
this occurs when the domain has sharp reentrant corners, and some illustrative limit cases include the slit domain~\cite{veeser2012poincare} and the crossed bricks domain~\cite{licht2019smoothed}, % DONE: MV : find the examples in the paper by verfurth and veeser 
which contain finite element patches are not star-shaped with respect to any ball.

@@

% DONE: cite VVVV
In the Hilbert space case, $p=2$, and when the domain has a smooth boundary, the work of Guerini and Savo~\cite{guerini2004eigenvalue} shows that the Poincar\'e--Friedrichs constant for the gradient already estimates the corresponding constants for the curl and divergence operators. By duality, this also is an upper estimate of the Poincar\'e--Friedrichs constants for the gradient, curl, and divergence subject to Dirichlet, tangential, and normal boundary conditions, respectively, along the entire boundary. 
% These comparisons~\eqref{math:intro:guerinisavo} are restricted to convex smoothly bounded domains.

However, no such results are known over convex Lipschitz domains and for general Lebesgue exponents $1 \leq p \leq \infty$, which is why we rely on regularized potential operators as a remedy. % DONE: Theo : But -> However 
We follow closely the discussions by Costabel and McIntosh~\cite{costabel2010bogovskiui},
who study regularized Poincar\'e and Bogovski\u{\i}-type potential operators over domains star-shaped with respect to a ball. 
In comparison to their exposition, our variants of the regularized potential operators are simplified:
we only study them over convex domains and use simpler (that is, constant) weight functions. 
The resulting operator features generally lower regularity properties in comparison to the regularized potential in the literature;
however, their properties are sufficient for our purposes. We easily estimate their operator norms. 
We consider the latter outcome to be of independent interest. 
\todo{Theo : I believe Gallistl-Olkhovskiy also estimate the constant. They do star-shape and regularized stuff, so it's different, but we should keep that in mind and maybe reference them}.

In addition to that, we need to find potentials for the gradient, curl and divergence operators over a simplex subject to partial boundary conditions. 
Again, we want to address the entire range $1 \leq p \leq \infty$ of Lebesgue exponents. 
We are not aware of any explicit estimates in the literature and there are no regularized potential operators for these boundary conditions. 
The Poincar\'e--Friedrichs inequality subject to full boundary conditions is repurposed to prove Poincar\'e--Friedrichs inequalities for differential forms over simplices and subject to partial boundary conditions. 
For example, given a divergence-free vector field over a tetrahedron with vanishing normal trace along three of the tetrahedron's faces, 
we want to find the unique vector field potential that is the preimage under the curl operator and which has vanishing tangential trace along the same three faces. 
% the curl of a vector field over a tetrahedron with vanishes along, say, two of the tetrahedron faces, we want to find the unique vector field potential. % DONE : Theo : unclear sentence 
We achieve this by constructing an auxiliary problem subject to full boundary conditions.
\\

% Exterior calculus % DONE: MV recommends moving this down to finish the current line of thoughts 
\todo{Where to place this paragraph?}
Though we present our results in vector calculus, our main arguments are given in the formalism of exterior calculus~\cite{greub1967multilinear,lee2012smooth}. Exterior calculus is used ubiquitously in the mathematical literature of physics and engineering and has found widespread adoption in the theoretical and numerical analysis for vector-valued partial differential equations~\cite{hiptmair2002finite,gross2004electromagnetic,arnold2006finite,arnold2009geometric,arnold2010finite,demlow2014posteriori,licht2021local,arnold2021complexes}. Loosely speaking, exterior calculus is the calculus of antisymmetric tensor fields. The formalism is independent of the dimension and highlights underlying geometric structures common to the gradient, curl, and divergence operators.
%It also enables us to leverage on the rich literature of Sobolev spaces of differential forms.
For the purpose of our discussion, this formalism allows us to leverage results from a larger body of literature in differential geometry and functional analysis. 
% DONE: Theo : paragraph feels misplaced 
\\

% Future work % DONE: Theo : parts already mentioned ??? 
% Computable reliable estimates are important: 
% they quantify the fundamental stability properties of partial differential equations in vector analysis,
% such as the Hodge Laplace equation. 
Any upper bounds for the Poincar\'e--Friedrichs constant corresponds to a lower bounds for the non-zero eigenvalues of the scalar and vector Laplacian.
% Furthermore, their constants enter the stability and convergence theory of finite element methods. 
In numerical methods, upper bounds for the Poincar\'e--Friedrichs for the Poincar\'e--Friedrichs constant enter the stability and convergence theory of finite element methods,
and they lead to lower bounds for the spectrum of finite element matrices. 
There are several avenues for further research going from here.

@@

Related to the first of the aforementioned opportunities for improvement, we conjecture that the Guerini--Savo estimates, hitherto only known for the exterior derivative as a mapping between Hilbert spaces and over convex domains with smooth boundary, could be extended to the entire range of Lebesgue exponents $1 \leq p \leq \infty$ and to convex Lipschitz domains. We believe such estimates would yield considerably better bounds on the Poincar\'e--Friedrichs constants than the regularized potential operators. 
% We conjecture that the Poincar\'e--Friedrichs constant for the gradient operator still bounds the Poincar\'e--Friedrichs constants of the other instances of the exterior derivatives, as in \eqref{math:intro:guerinisavo}, when $1 \leq p \leq \infty$ and the domain is convex. 
On a related note, explicit estimates for the operator norms of regularized potential operators with different degrees of smoothing are of general interest. 
These topics remain for future research.

@@

When $\calT$ is a triangulation and $T \in \calT$, then $\patch_{\calT}(T)$ denotes the \emph{local patch} or \textit{local star} of $T$, 
which is the simplicial subcomplex of $\calT$ that contains all supersimplices of $T$ and their subsimplices. 
We write $\carapace_{\calT}(T)$ for the subset of the local patch whose members do not contain $T$ itself. 
Formally,
\begin{gather*}
    \patch_{\calT}(T) := \bigcup_{ T' \in \supsimplex(\calT,T) } \subsimplex(T'),
    \qquad 
    \carapace_{\calT}(T) := \bigcup_{ \substack{ T' \in \patch_{\calT}(T) \\ T \nsubseteq T' } } \subsimplex(T').
\end{gather*}
We write $U_T := | \patch_{\calT}(T) |$ for the underlying set of the local patch. 
A crucial observation is the following.

@@

We introduce a specific notion of connectivity. 
Given an $n$-dimensional simplicial complex $\calT$, 
we call $n$-simplices $S,S' \in \calT$ \emph{strongly connected in $\calT$} if there exists a sequence $S_0=S,S_1,\dots,S'=S_m \in \calT$ such that $S_{i} \cap S_{i-1}$ is a face of both $S_{i}$ and $S_{i-1}$ for all $1 \leq i \leq m$. % TODO: Theo suggests reverse order of that sequence 
We call such a sequence a \emph{strong path} from $S$ to $S'$ in $\calT$. 
Clearly, strongly connected in $\calT$ is an equivalence relation among simplices. 
A \emph{strongly connected component} of $\calT$ is an equivalence class under this equivalence relation, 
and we call $\calT$ \emph{strongly connected} if it has only one strongly connected component.

@@

We collect examples for Poincar\'e and Poincar\'e--Friedrichs inequalities for the important special case of convex domains; 
see also~\cite[Lemma~3.24]{ern2021finite} for a short overview. 
Over convex bounded domains, we have the Poincar\'e inequalities~\cite{bebendorf2003note,acosta2004optimal} 
\begin{align}\label{math:acostaduran}
    \| u - u_{\Omega} \|_{L^{1}(\Omega)}
    \leq 
    \frac{\diam(\Omega)}{2}
    \| \nabla u \|_{L^{1}(\Omega)}
    ,
    \quad 
    \forall 
    u \in W^{1,1}(\Omega)
    ,
    \\
    \| u - u_{\Omega} \|_{L^{2}(\Omega)} \label{math:bebendorf}
    \leq 
    \frac{\diam(\Omega)}{\pi}
    \| \nabla u \|_{L^{2}(\Omega)}
    ,
    \quad 
    \forall 
    u \in W^{1,2}(\Omega)
    .
\end{align}
These two estimates are the best possible Poincar\'e inequalities in the cases $p=1$ and $p=2$, respectively, in terms of the diameter alone. 
Upper bounds for the Poincar\'e constant over convex domains with $1 < p < \infty$ are known in the literature~\cite[Theorem~1.1, Theorem~1.2]{chua2006estimates}:
\begin{align}\label{math:chuawheeden}
    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
    \leq 
    C_{{\rm P},{\rm CW},p}
    \diam(\Omega)
    \| \nabla u \|_{L^{p}(\Omega)}
    ,
    \quad 
    \forall 
    u \in W^{1,p}(\Omega)
    ,
\end{align}
where we use an upper bound by Chua and Wheeden:
\begin{align*}
    C_{{\rm P},{\rm CW},p} 
    := 
    \sup\limits_{ v \in C^\infty([0,1]) \setminus \bbR } 
    \frac{ 
        \| v - v_{[0,1]} \|_{L^{p}([0,1])} 
    }{ 
        \| \nabla v \|_{L^{p}([0,1])} 
    }
    \leq 
    \sqrt[p]{p} 2^{1-\frac 1 p}
    =
    2
    \left( \frac p 2 \right)^{\frac 1 p}
    .
\end{align*} % DONE: Theo : following sentence : which upper bound ?
Note that $C_{{\rm P},{\rm CW},p}$ is generally not optimal among the upper bounds that only depend on the domain diameter and the Lebesgue exponent.
As discussed above, these Poincar\'e inequalities imply Poincar\'e--Friedrichs inequalities.

@@

In this section we address the stepwise computable estimate of Poincar\'e--Friedrichs constants of triangulated domains. 
As a preparatory step, given a gradient vector field, we can reconstruct the original scalar function up to a constant by a well-understood procedure: after fixing a starting point, we integrate the gradient vector field along lines emanating from that starting point. This defines a scalar potential. 
This serves as our inspiration for estimating the Poincar\'e constant over triangulated domains, which we achieve by an explicit construction of scalar potentials: 
after fixing a starting triangle, we construct a scalar potential for a given gradient vector field on larger and larger simplicial neighborhoods. 
The basic idea has appeared in the different variants before, for instance recently in \cite{Ern_Voh_p_rob_3D_20, Chaum_Voh_p_rob_3D_H_curl_23, Voh_loc_glob_H1_24}.
\\

@@

% TODO: Theo : Should shape measures and their discussion be put into the previous section ?

@@

\begin{example}
    Any simplex $T$ trivially has a shelling. The boundary complex $\partial \calT(T)$ has a shelling:
    in fact, any enumeration of the boundary faces of $T$ constitutes a shelling.
\end{example}
\begin{example}
    The standard triangulation of the $3$-dimensional cube by six tetrahedra, the Kuhn triangulation~\cite{kuhn1960some}, is shellable, as are its higher-dimensional generalizations.\footnote{We remark that Kuhn attributes this triangulation to Lefschetz~\cite{lefschetz2015introduction}.}
\end{example}

@@

        A similar argument applies to the triangulation $\calR'$. 
        We conclude that $\Xi$ is bi-Lipchitz. 
        \color{black}

        \item 
        \color{red}
        We collect several geometric facts.
